
\subsection{LLM-Based Agent Systems}

The development of LLM-based autonomous agents has progressed rapidly from prompting-level techniques to fully integrated production systems.
Early work focused on augmenting a single LLM call with structured reasoning.
ReAct~\citep{react} interleaves chain-of-thought reasoning~\citep{cot} with environment actions, enabling models to ground their plans in observed feedback.
Reflexion~\citep{reflexion} extends this paradigm by introducing verbal self-reflection: after each trial the agent critiques its own trajectory and carries the critique forward, yielding substantial gains on sequential decision-making benchmarks.

Moving beyond single-turn prompting, AutoGPT~\citep{autogpt} demonstrated that an LLM can autonomously decompose a high-level goal into sub-tasks, execute them through tool calls, and iterate until completion, sparking widespread interest in fully autonomous agents.
MetaGPT~\citep{metagpt} shifted the focus to multi-agent collaboration, encoding domain-specific Standard Operating Procedures (SOPs) into the communication protocol at design time so that specialized agents coordinate through structured message passing rather than free-form dialogue.

Software engineering has emerged as a primary proving ground.
Devin~\citep{devin}, introduced as the first AI software engineer, couples long-horizon planning with an integrated development environment.
SWE-agent~\citep{sweagent} formalizes the notion of an \emph{Agent--Computer Interface} (ACI), demonstrating that purpose-built commands for file navigation and editing significantly outperform raw shell access.
OpenHands~\citep{openhands} provides an open-source platform unifying multiple agent architectures with a shared runtime, complemented by the OpenHands SDK~\citep{openhands_sdk} for rapid agent development.

Most recently, a wave of product-level systems has pushed the frontier of agent capabilities.
Claude Code~\citep{claudecode} adopts a single-threaded master loop with approximately 24 built-in tools, relying on compaction-based context management that triggers summarization when utilization reaches roughly 92\% of the context window.
OpenAI Codex~\citep{codex} deploys an RL-optimized coding agent in isolated cloud sandboxes, emphasizing safe parallel execution.
Manus~\citep{manus} introduces a three-agent architecture---planner, executor, and verifier---built around the CodeAct paradigm in which executable Python code serves as the universal action format.
OpenClaw~\citep{openclaw_rl} takes a messaging-platform-centric approach, centering agent interaction on a skills marketplace and attracting broad community adoption.

Despite this rapid progress, the vast majority of existing systems target single-session task completion or are tailored to a specific domain such as software engineering.
Few address the challenge of long-term autonomy with a systematic optimization of context efficiency.
GenericAgent is designed to fill precisely this gap.

\subsection{Memory Systems for Agents}

Effective memory management is critical for agents that must operate over extended horizons, yet existing approaches exhibit notable limitations.
MemGPT~\citep{memgpt} draws an analogy to operating-system virtual memory, maintaining a two-tier architecture in which the LLM's context window serves as ``main memory'' (RAM) and an external database acts as ``disk.''
A paging mechanism swaps information between the two tiers on demand, but the approach inherits the complexity of page-fault handling without mechanisms to verify the integrity of what is stored.

A-MEM~\citep{amem} takes inspiration from the Zettelkasten note-taking method, organizing memories as a dynamically evolving graph with semantic links between atomic notes.
While the graph structure supports rich associative retrieval, the system lacks mechanisms to prevent hallucinated or stale information from contaminating the memory store over time.

Among production systems, Claude Code~\citep{claudecode} persists memory as flat Markdown files and triggers compaction---a summarization pass that condenses the conversation---when context utilization approaches its ceiling.
Manus~\citep{manus} maintains a chronological event stream as working memory and offloads longer-term state to file-based artifacts such as \texttt{todo.md} for plan tracking.
Both designs are predominantly append-only: new information is accumulated but rarely condensed, compressed, or actively verified against ground truth.

A common shortcoming across these systems is the absence of strict verification mechanisms that guard against hallucination contamination of the memory store.
Updates are largely additive, and no system performs active condensation that distills accumulated knowledge into progressively denser representations.
GenericAgent addresses these gaps through its L0--L3 hierarchical memory architecture and a ``No Execution, No Memory'' verification principle that conditions every memory update on an observed action outcome, ensuring that only empirically validated information enters the persistent store.

\subsection{Self-Evolution and Experience Accumulation}

A growing body of work investigates how agents can improve autonomously by accumulating and leveraging experience.
Voyager~\citep{voyager} introduced the first LLM-based lifelong learning agent, constructing an ever-growing library of executable skills within the Minecraft environment; each skill is a verified JavaScript program that the agent can compose to tackle increasingly complex tasks.

A recent survey on self-evolving agents~\citep{selfevolvesurvey} provides a comprehensive taxonomy along three axes: \emph{what} to evolve (model parameters, memory, or tool repertoire), \emph{when} to evolve (intra-test-time versus inter-test-time), and \emph{how} to evolve (using scalar or textual feedback).
Within this taxonomy, several concrete methods have been proposed.
EvolveR~\citep{evolver} performs offline self-distillation of successful trajectories into strategic principles, which are then retrieved online to guide future decisions.
FLEX~\citep{flex} builds a structured experience library through continual reflection on both successes and failures, selecting relevant past experiences at inference time.
AgentEvolver~\citep{agentevolver} represents experience as structured knowledge units expressed in natural language and injects them into the agent's context for in-context learning.
The self-evolving lifelong learning framework~\citep{selfevolvinglifelong} decomposes the evolution process into three stages---experience exploration, skill learning, and knowledge internalization---providing a principled progression from raw observations to reusable capabilities.

Despite their diversity, existing self-evolution approaches share a common limitation: they distill experience exclusively into textual guidelines---natural-language summaries, principles, or structured notes.
None take the further step of codifying distilled experience into executable programs, thereby missing an opportunity for order-of-magnitude reductions in token cost.
An SOP that requires hundreds of tokens to describe in prose can often be implemented as a short function consuming only a handful of tokens to invoke.
GenericAgent's three-stage evolution pipeline---from natural-language experience to structured SOPs to executable code and reusable skills---bridges this gap, enabling progressively denser and more efficient representations of accumulated knowledge.

\subsection{Tool Design and Context Engineering}

Tool augmentation has become a standard technique for extending LLM capabilities.
Toolformer~\citep{toolformer} demonstrated that language models can learn to insert API calls into their own generations, while Gorilla~\citep{gorilla} and ToolBench~\citep{toolbench} address the challenge of selecting from large-scale tool repositories with hundreds or thousands of available APIs.
Function calling interfaces, initially popularized alongside GPT-4~\citep{gpt4} and subsequently adopted across providers, now provide the dominant paradigm for structured tool invocation in production systems.

The Manus system~\citep{manus} pushes this further with its CodeAct paradigm, in which executable Python code serves as a universal action format---subsuming individual tool calls within a more expressive programming abstraction.
On the design-philosophy side, Anthropic's ``Building Effective Agents''~\citep{anthropic_agents} and ``Context Engineering''~\citep{anthropic_context} documents offer the most systematic industry articulation of context efficiency principles to date, advocating system prompts written at the right level of abstraction, token-efficient tool definitions, just-in-time information retrieval, and aggressive compaction of historical context.

In practice, however, existing systems tend to address capability gaps by adding specialized tools: Claude Code~\citep{claudecode} ships with approximately 24 built-in tools, and OpenHands~\citep{openhands} exposes a rich and extensible toolset.
Each additional tool definition consumes context tokens for its schema, description, and usage examples, creating a tension between capability breadth and context efficiency.

Web browsing presents a particularly acute instance of this tension.
Vision-based approaches such as Anthropic's Computer Use~\citep{computeruse} operate on screenshot pixels, while DOM-based methods parse the page's HTML or accessibility tree.
WebArena~\citep{webarena} and Mind2Web~\citep{mind2web} have established standard benchmarks for evaluating web agents, revealing that both raw HTML and accessibility-tree representations contain substantial irrelevant information---navigation bars, decorative elements, tracking scripts---that dilutes the context with low-density tokens.

GenericAgent takes a fundamentally different approach.
Rather than expanding the tool repertoire, it defines a minimal atomic set of only seven tools whose principled composition achieves full environmental control.
Combined with DOM-level content compression that strips irrelevant markup before it enters the context window, this design simultaneously minimizes tool-definition overhead and maximizes the information density of web interaction observations.
