We have presented GenericAgent (GA), a general-purpose LLM agent system whose architecture is organized around a single guiding principle: \emph{context information density maximization}.
Every design decision---from the L0--L3 hierarchical memory that loads only task-relevant information on demand, through the reflection-driven self-evolution pipeline that compresses experiential knowledge into increasingly compact representations, to the seven minimal atomic tools and the simplified HTML browser control---serves to ensure that each token in the finite context window carries maximal value for the current reasoning step.
Together, these four contributions form a coherent system that enables sustained, long-horizon autonomous operation across interactive, task-driven, and event-triggered scenarios.

A key insight underlying GA is that self-evolution operates entirely at inference time, requiring no fine-tuning of the base model.
By progressively transforming free-form experience into structured SOPs, then into executable code, and ultimately into reusable skills, the system achieves order-of-magnitude reductions in the number of tokens needed to represent recurring operational knowledge, directly realizing the density maximization objective.

Several limitations merit discussion.
First, the effectiveness of GA is ultimately bounded by the reasoning and instruction-following capabilities of the underlying language model; advances in base model quality translate directly into improved agent performance, but current ceilings remain binding for the most complex tasks.
Second, the hierarchical memory taxonomy, while general in design, requires initial configuration effort to align with new application domains.
Third, the self-evolution mechanism yields the most pronounced gains for tasks exhibiting regular, repeatable structure; highly novel or one-shot tasks benefit less from experience compression.
Finally, the browser control subsystem assumes the availability of a Chrome extension for DOM observation, which introduces a deployment dependency.

Looking ahead, we identify several promising directions for future work.
Multi-agent collaboration with shared hierarchical memory pools could enable teams of GA instances to pool experience and divide labor on complex workflows.
Cross-task knowledge transfer---automatically migrating skills and SOPs across related but distinct domains---would further amplify the returns of self-evolution.
Formal evaluation metrics for context information density, beyond proxy measures such as token counts, are needed to rigorously benchmark density-driven agent designs.
Finally, integration with emerging agent communication protocols would allow GA to interoperate seamlessly within broader multi-agent ecosystems.
